---
title: "Feedback From The `r tools::toTitleCase(english::ordinal(params$cohort))` Cohort"
author: "School of Government and Politics"
date: "`r format(Sys.Date(), format = '%e %B, %Y')`"
params:
  cohort: 5
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, cache=FALSE, include = FALSE}
knitr::read_chunk(here::here("scripts/analysis/eval.R"))
```

```{r ext-setup, include=FALSE}
```

## Participation in the evaluation
```{r respondents}
```

```{r respondents-table}
```

```{r respondents-chart}
```

```{r attendance-respondents}
```

## Analysis of Key Responses
### Q1. Was the module content too challenging for an average learner to understand?
```{r challenging}
```

```{r module-challenging}
```

### Q3. Did the ideas expressed in delivering the module seem too distant from your experience?
```{r too-distant}
```

```{r module-too-distant}
```

### Q4. How would you rate the duration of the class?
```{r duration}
```

```{r module-duration}
```

### Q5. How long would you recommend that class session lasts?
```{r recommend-dur}
```

### Q7. Overall, how would you rate the communication skills of the facilitator?
```{r fac-comm}
```

```{r module-fac-comm}
```

### Q9.	Did you feel comfortable expressing yourself to your facilitator?
```{r fac-comfort}
```

```{r module-fac-comfort}
```

### Q10. Were your training expectations fulfilled?
```{r expectations}
```

```{r module-expectations}
```
