---
title: "Review of Data from SOGP Ethics & Values Course"
author: "Victor Ordu"
Date: "`r Sys.Date()`"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
params:
  cohort: 5
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(labelled)
library(flextable)

source(here::here('scripts/helpers.R'))

opts_chunk$set(echo = FALSE, warning = FALSE)

reg <- read_cohort_dbtable("registration", params$cohort)
m.reg <- reg %>%
  as_tibble() %>%
  mutate(hindrance = str_split(hindrance, "\\n") %>% map(sort)) %>%
  mutate(country = str_replace(country, "Nigria|Rivers.+", "Nigeria") %>%
           str_remove("Wales\\,\\s") %>% 
           str_replace("Country", ""))

## Create new columns with the multiple responses split up and
## spread out into them.
multichoice <- c("Data", "Network", "None", "Schedule", "Device")
for (i in multichoice) {
  m.reg[[i]] <- map_chr(m.reg$hindrance, function(elem) {
    val <- grep(i, elem, ignore.case = TRUE, value = TRUE)
    if (!length(val))
      return(NA_character_)
    val
  })
  lbl <- na.omit(unique(m.reg[[i]]))
  attributes(lbl) <- NULL
  m.reg[[i]] <- ifelse(is.na(m.reg[[i]]), 0, 1)
  var_label(m.reg[[i]]) <- lbl
}
m.reg$hindrance <- NULL

## The Evaluation questions (short form will be requested for labels)
qry.ques <- "SELECT question_short FROM eval_ques;"
ques <- unlist(query_data(qry.ques))
ques <- unname(ques[-2])  # Question was removed

categorical <-
  c(
    "challenging",
    "too_distant",
    "rating_dur",
    "fac_comm",
    "fac_expert",
    "fac_comfort",
    "fulfil_expect"
  )

## The post-module evaluation data proper
eval.dat <- read_cohort_dbtable('evaluation', params$cohort)
eval.dat <- eval.dat %>% 
  select(-cohort_id) %>% 
  mutate(across(all_of(categorical), factor)) %>% 
  mutate(across(where(~ any(grepl("^(Yes|No)$", .x))), ~ factor(.x, c("Yes", "No")))) %>% 
  mutate(rating_dur = factor(rating_dur, c("Too short", "Just right", "Too long"))) %>% 
  mutate(fac_expert = factor(fac_expert, c("Low", "Average", "Acceptable", "Good", "High"))) %>% 
  mutate(fac_comm = factor(fac_comm, c("Low", "Average", "High")))

lbls <- c("Module", "Time", ques)
var_label(eval.dat) <- lbls


## Functions
barchart <- function(data, var, col = "blue", disaggregate = FALSE, flip = FALSE) {
  stopifnot(is.data.frame(data), is.character(var))
  lab <- var_label(data[[var]])
  if (is.null(lab) || is.na(lab))
    lab <- var
  p <- data %>% 
    mutate(module_name = paste("Module", module_id)) %>% 
    ggplot(aes_string(var)) +
    geom_bar(fill = col) + 
    labs(x = lab) +
    theme(axis.text = element_text(face = 'bold'))
  if (flip)
    p <- p + coord_flip()
  if (disaggregate)
    p <- p + facet_wrap(vars(module_name))
  print(p)
}

## Gets the data from a flextable object
get_ft_data <- function(t) {
  stopifnot(inherits(t, "flextable"))
  t$body$dataset
}

## Fetches a specific value from a flextable object
get_value <-
  function(data,
           base.col = NULL,
           item = NULL,
           value,
           stat = NULL) {
    if (inherits(data, 'flextable'))
      data <- get_ft_data(data)
    stopifnot(is.data.frame(data))
    nms <- names(data)
    col <- grep(value, nms, ignore.case = TRUE)
    if (!length(col))
      stop("No match fo the regular expression 'value'")
    if (length(col) > 1L)
      stop("The regular expression 'value' should match just one column")
    base.col <- data[[grep(base.col, nms, ignore.case = TRUE)]]
    if (!is.null(stat)) {
      base.nms <- if (is.factor(base.col))
        levels(base.col)
      else
        base.col
      val.col <- structure(data[[col]], names = base.nms)
      ans <- if (stat == "sort")
        do.call(stat, list(val.col))
      else
        do.call(stat, list(val.col, na.rm = TRUE))
      if (stat == 'max' || stat == 'min') {
        are <- val.col %in% ans
        ii <- which(are)
        ans <- rep(ans, length(ii))
        names(ans) <- base.col[ii]
      }
    }
    if (!is.null(item)) {
      row <- grep(item, base.col, ignore.case = TRUE)
      if (!row)
        stop("No row of 'base.col' matched the regular expression 'item'")
      ans <- data[row, col]
    }
    if (grepl("perc", nms[[col]], ignore.case = TRUE)) {
      nn <- names(ans)
      ans <- if (ans)
        paste0(round(ans, 1), "%")
      else
        "none"
      names(ans) <- nn
    }
    ans
  }
```

# Introduction
```{r intro-inline}
qry.txt <- "SELECT %s FROM cohorts wHERE id = 5;"
start.date <- as.character(query_data(sprintf(qry.txt, "start_date")))
end.date <- as.character(query_data(sprintf(qry.txt, "end_date")))
my_date <- function(dt) format(as.Date(dt), "%d %B, %Y")
```

This is a review of the data collected for the School of Government and Politics (SOGP) Ethics and Values Course, focusing on Cohort `r params$cohort`, which ran from `r my_date(start.date)` to `r my_date(end.date)`..

# Analysis of the Data
## Registrations

```{r reg-inline}
att <- filter(reg, attended == 1)
total <- nrow(reg)
perc.att <- round((num.att <- nrow(att)) / total * 100, 1)
countries <- unique(m.reg$country)
countries <- countries[countries != ""]
```

A total of `r total` persons registered for the course, out of whom `r num.att` actually attended any of the modules (i.e. `r perc.att`%). Registrations came from `r length(countries)` countries, namely `r combine_words(sort(countries))`.

```{r reg-plot, fig.cap="Proportion of Registered Learners Who Attended the Course"}
pie(
  c(total - num.att, num.att),
  radius = 1.05,
  col = c("red", "green"),
  labels = c(
    paste0("Not attended (", 100 - perc.att, "%)"),
    paste0("Attended (", perc.att, "%)")
  )
)
```

Those that registered were asked to indicate possible factors that could hinder them from participating in the programme. These include a tight schedule, phone or device issues, network issues, and lack of data. 

```{r hindrances-table, tab.cap = "Hindrances to participation"}
dt <- ufs::multiResponse(m.reg, multichoice)
ft <- flextable(dt) %>% 
  set_header_labels(Option = "Response") %>% 
  colformat_double(j = 3:4, digits = 1) %>% 
  bold(i = 6) %>% 
  hline(i = 5:6) %>% 
  width(width = 1)
ft
```

Only `r get_value(ft, "option", "device", "percent.+response")` of the respondents indicated that issues with their device could be a hindrance, while the other potential hindrances ranged from 22 - 24% in importance.

```{r hindrances-plot, fig.cap="Possible Hindrances to Participation"}
ft$body$dataset %>% 
  filter(Option != "Total") %>% 
  rename(Hindrance = Option) %>% 
  ggplot(aes(Hindrance, `Percentage of (381) cases`)) +
  geom_col(fill = "black", col = "red") +
  scale_x_discrete(aesthetics = "Hindrance", palette = "Set1")
```

## Responses to Evaluation Questionnaire
After each module, an evaluation questionnaire was provided for learner feedback. Below is the summary of the analysis of their responses.

### Difficulty of module content

```{r challenging-course, fig.cap="Course content was challenging"}
barchart(eval.dat, "challenging", col = "red")
```

```{r challenging-modules, eval=FALSE, fig.cap="Module content found challenging"}
barchart(eval.dat, "challenging", col = "red", disaggregate = TRUE)
```

### Ideas presented were distant

```{r distant-course, fig.cap="Course content adjudged 'too distant'"}
barchart(eval.dat, "too_distant")
```

```{r distant-module, fig.cap="Modules adjudged 'too distant "}
barchart(eval.dat, "too_distant", disaggregate = T)
```


### Rating on class duration

```{r duration, fig.cap="Adequacy of class duration"}
barchart(eval.dat, 'rating_dur', col = "darkgreen")
```
```{r duration-faceted, eval=FALSE, fig.cap="Adequacy of each module's duration"}
barchart(eval.dat, 'rating_dur', col = "darkgreen", disaggregate = TRUE)

```

### Recommended duration of class

```{r recommended-duration-data}
recdur <- table(eval.dat$recomm_dur)
recdur <- structure(as.numeric(recdur), names = names(recdur))
```

Most of the respondents recommended a `r names(recdur)[which.max(recdur)]`-hour duration for the course modules.

```{r recommended-duration-plot, fig.cap="Recommended Duration of Module Sessions"}
dotchart(
  recdur,
  pch = 18,
  color = "blue",
  lcolor = "red",
  cex = 1.2, 
  xlab = "No. of Responses",
  ylab = "Proposed Length (hours)"
)
```

### Communication skills of facilitator
```{r fac-comm, fig.cap="Communicationi Skill of the facilitators"}
barchart(eval.dat, 'fac_comm', col = "brown", disaggregate = TRUE)
```

### Facilitator's expertise
```{r}
barchart(eval.dat, 'fac_expert', col = "purple", disaggregate = TRUE, flip = TRUE)
```

### Feel comfortable expressing oneself to facilitator
```{r}
barchart(eval.dat, 'fac_comfort', col = "cyan")
```

### General comments
Notable comments from participants on the course and its delivery include:

```{r comments, eval= Sys.Date() < "2021-08-31"}
cat('
> "It was an amazing and value packed module. I am better armed and charged to intentionally start from my immediate sphere of influence, collaborate, organise and pressure the systems for transparency and accountability"


> "Corruption module holistically address African leadership system and reasons for the under development" 


> "It was just so on point and has helped sharpen my eyes of understanding on the essential role civil participation play in ensuring sustainable development. We have to demand transparency at ensure our leaders are accountable at every sphere of governance. It starts with me! " 

')
```

```{r comments-2, eval= params$cohort == 5, results='asis'}
cat('
> *"This topic was so beautiful, simple and well understood, because it dealt with our everyday life experience."*

> *"This should really be taught in all schools in Nigeria to also aid National development"*

> *"Very useful in understanding how citizens can carry their civic responsibilities ethically."*

> *"It changed my view generally in a positive way. Thanks."*

> *"I think is good but I have to go through it for better understanding."*

> *"With the class coming to an end, I have got it that, I belong to the right ground for growth."*

> *"I was able to improve my capacity building. The training was very interactive, educative and interesting."*
')
```


### Observations/Recommendation 
Some of the course participants also made some observations and recommendations related to some issues they encountered:

```{r recommendations, eval= Sys.Date() < "2021-08-31"}
cat('
1. The structure of the evaluation needs to be reviewed, but for future courses, since this one has already gone quite far. Many of the questions asked cannot be usefully analysed as they are presently.

2. The reporting needs to be structured in such a way that the reporting can be in a module by module basis.

3. There were some repetitions i.e. some students responded more than once for the same module.

4. It seems only few of the students completed the evaluation. A way should be devised to ensure close to 100% response rate. In this light, the evaluation data should equally be accompanied by attendance.

5. The evaluation should be anonymous. This will also encourage people to complete it. This change should be made to the form **now**.

6. The charts are still rudimentary, but will have to be improved upon over time, due to time constraints.
    
')
```


```{r student-recommend, eval = params$cohort == 5, results='asis'}
cat('
> *"The broadband can be improved to assist the network connectivity."*

> *"My concern is the problem of network, it is really not good for better assimilation of knowledge"*

> *"I didnt get the best part of this module, there was power outage."*

> *"I\'ll be glad if the management can consider sending a soft copy of the course module to us for download and future reference."*
')
```
